Towards human SuperEEG

### 2018-10-05 paper/main.tex
corrected latex error

\newcommand{\taskrecon}{S1}
\newcommand{\per_exp_taskrecon}{S2}
\newcommand{\per_exp_corrmaps}{S3}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent datset and found
similar results (Fig.~\ref{corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beynd the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.

>>>>

\newcommand{\taskrecon}{S1}
\newcommand{\perexptaskrecon}{S2}
\newcommand{\perexpcorrmaps}{S3}

@@

As a stricter benchmark, we compared the quality of these
across-participant reconstructions (i.e., computed using a correlation
model derived from other patients' data) to reconstructions generated
using a correlation model trained using the in-patient's data.  In
other words, for this within-patient benchmark analysis we estimated
$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
using recordings from all of that patient's electrodes except at the
location we were reconstructing.  These within-patient reconstructions
serve as an estimate of how well data from all of the other electrodes
from a single patient may be used to estimate held-out data.  This
allows us to ask how much information about the activity at a given
electrode might be inferred through (a) volume conductance or other
sources of ``leakage'' from activity patterns measured from the
patient's other electrodes and (b) across-electrode correlations
learned from that single patient.  As shown in
Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
within-patient correlations was centered well above zero (mean: XXX;
$t$-test comparing mean of distribution of $z$-transformed
per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
However, the across-patient correlations were substantially higher
($t$-test comparing average $z$-transformed within versus across
patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
especially conservative test, given that the across-patient SuperEEG
reconstructions exclude (from the correlation matrix estimates) all
data from the patient whose data is being reconstructed.  We repeated
each of these analyses on a second independent datset and found
similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,
that when reconstructing held-out data from a given patient
correlation models derived from \textit{other} patient's data yield
higher reconstruction accuracy than correlation models derived from
that patient, has two important implications.  First, it implies that
distant electrodes provide additional predictive power to the data
reconstructions beynd the information contained solely in nearby
electrodes.  (This follows from the fact that each patient's
electrodes are implanted in a unique set of locations, so for any
given electrode the closest electrodes in the full dataset are likely
to come from the same patient.)  Second, it implies that the spatial
correlations derived from the SuperEEG algorithm are, to some extent,
similar across people.
